Visualizing Multivariate PDFs

### 2016-08-24 sections/seperable.tex
hist, vase, violin

\begin{figure}
%%\includegraphic{Mcgill} #annottate figure with highlighted line for the notches!
\label{fig:notched}
\end{figure}
The box-plot was then expanded out from descriptive statistics to facilitatting
inferential deduction through the notched boxplot. \cite{mcgill1978} The notched boxplot
arose as an expansion of indicating sample size through the width of the box,
which is a technique that only works well for relatively small sample sizes (\<
1000), at larger scales the widths are about equal. Instead, notches, as seen
in Figure~\ref{fig:notched}, are used to indicate the confidence level of the
median for that box. The medians are statistically different from each other at
the 95\% confidence level if the notches do not overlap. In
Figure~\ref{fig:notched}, all the notches overlap %%annotate figure with what
%%overlapping region means
and so the difference in telephone bills is not-significant, but there's a
statistically significant difference between the 11-15 and over 15 groups. Notches may extend
beyond the box edges, and sometimes the width technique is incorporated back
into the notched boxpplot such that the confidence can be grounded in sample
size. The notches in Figure~\ref{fig:notched} are computed assuming a gaussian
distribution, but many authors \cite{x,y,z} discuss ways to compute notches for
non-gaussian distributions. 
\end{align}

>>>>

\begin{figure}
%%\includegraphic{Mcgill} #annottate figure with highlighted line for the notches!
\label{fig:notched}
\end{figure}
The box-plot was then expanded out from descriptive statistics to facilitatting
inferential deduction through the notched boxplot. \cite{mcgill1978} The notched boxplot
arose as an expansion of indicating sample size through the width of the box,
which is a technique that only works well for relatively small sample sizes (\<
1000), at larger scales the widths are about equal. Instead, notches, as seen
in Figure~\ref{fig:notched}, are used to indicate the confidence level of the
median for that box. The medians are statistically different from each other at
the 95\% confidence level if the notches do not overlap. In
Figure~\ref{fig:notched}, all the notches overlap %%annotate figure with what
%%overlapping region means
and so the difference in telephone bills is not-significant, but there's a
statistically significant difference between the 11-15 and over 15 groups. Notches may extend
beyond the box edges, and sometimes the width technique is incorporated back
into the notched boxpplot such that the confidence can be grounded in sample
size. The notches in Figure~\ref{fig:notched} are computed assuming a gaussian
distribution, but many authors \cite{x,y,z} discuss ways to compute notches for
non-gaussian distributions.

\begin{figure}
%%two figs a and b with a shared caption...
%%\includegraphics{benjamini}
\label{fig:histplot}
\label{fig:vase}
\end{figure}

Because the box-plot does not give any indication of how data is distributed
inside the box or along the whiskers, the histplot and vaseplot were introduced to indicate
the density of the data\cite{benjamini1988}. As shown in
Figure~\ref{fig:histplot} the histplot seperates the box
into  5 bins and scales the width of that section of the box based on the
number of values in that bin; it's essentially a rotated histogram. The
vaseplot, shown in Figure~\ref{fig:vase} removes the bins and is instead based
on the estimated density at that point in the data. The specific shape is
dependent on what sort of density estimation method is used, such as kernal
estimation or nearest neighbor estimation \cite{chambers1983}. The
violinplot \cite{hintz1998} expands this concept further by representing the
width using the density-trace method proposed by Chambers
et. al \cite{chambers1983}%%is density trace the same as a pdf?
